An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-18 answer-to-reviewers/answer-to-reviewers.tex

We thank the reviewers for their time, consideration and thoughtful comments. Our article has been amended
according to their recommendations. Changes in the text are highlighted in red. In addition, our replies follow.

\section{Reviewer \#1}

\paragraph{This is an interesting contribution to digital processing of images. Alternative approaches to discretization of elastica based on polygonal approximations for discrete elastica and their convergence issues could be mentioned for comparison}

~\\ In section 5, we indeed compare our segmentation model with the
work of \cite{schoenemann09linear}, which uses a polygonal
approximation of discrete elastica. In this work, the curvature is
estimated with a simple formula involving angle and edge lengths at
polygon vertices as proposed in \cite{bruckstein96}. This discrete
elastica problem with fixed end-points is proven to be
$\Gamma$-convergent toward the continuous elastica problem in
\cite{bruckstein01}. However it is not straightforward to include
image date term in these work, since the optimization variables of the
polygonal approximation are not related to the digital domain. For
instance, one could also use splines approximation with exact
curvature information and the same kind of approach would have the
same pros and cons.

We remark that our approach never leaves the digital domain. In other
words, it is purely digital and it does not rely on any curve
representation. With this approach, all the optimization variables are
related to the digital domain, and we can thus optimize in the same
process data terms and elastica terms. Hence there is no alternate
minimization involved.

Finally, the notions of multigrid convergence and $\Gamma$-convergence
are not easily comparable. The former concerns the accuracy of an
estimation, the latter concerns a sequence of minimizers. The former
is specifically designed for digital data, hence more appropriated in
our case as our main objects of interest are digital images.  ~\\

### 2019-12-19 jmiv.tex
Improve plots visibility

\begin{figure}[!h]
\center
\subfloat[\label{}]{\includegraphics[scale=0.6]{images/local_search/square.eps}}
\subfloat[\label{}]{\includegraphics[scale=0.6]{images/local_search/flower.eps}}
\caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}. \revision{The final shape has energy value closer to the optimal value $2\pi/5$ (thin horizontal dashed line)}.}
\label{fig:plot-elastica-local-search}
\end{figure}

>>>>

\begin{figure}[!h]
\center
\subfloat[\label{}]{\includegraphics[scale=0.32]{images/local_search/square.eps}}
\subfloat[\label{}]{\includegraphics[scale=0.32]{images/local_search/flower.eps}}
\caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}. \revision{The final shape has energy value close to the optimal value $2\pi/5$ (thin horizontal dashed line)}.}
\label{fig:plot-elastica-local-search}
\end{figure}
